---
title: "Capstone Week 1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Library
```{r, warning=FALSE}
library(readr)
library(lubridate)
library(ggplot2)
library(dplyr)
library(readr)
library(stringr)
library(ggpubr)
```

# Read Data
```{r, message=FALSE}
en_US_twitter<-read_lines ("C:/Users/slc404/OneDrive - Sherwin-Williams/Rprojects/Coursera/Data Science Capstone/final/en_US/en_US.twitter.txt")
en_US_news<-read_lines ("C:/Users/slc404/OneDrive - Sherwin-Williams/Rprojects/Coursera/Data Science Capstone/final/en_US/en_US.news.txt")
en_US_blogs<-read_lines ("C:/Users/slc404/OneDrive - Sherwin-Williams/Rprojects/Coursera/Data Science Capstone/final/en_US/en_US.blogs.txt")
```

# Basic Summary 
A basic summary of word count, line count, and character count was conducted. Twitter file has more lines than blog or news. While news has the highest average word count. Blog has the highest avereage character count. 
```{r, message=FALSE}
#Word Count
blog_word_count<-as.data.frame(str_count(en_US_blogs, boundary("word")))
twitter_word_count<-as.data.frame(str_count(en_US_twitter, boundary("word")))
news_word_count<-as.data.frame(str_count(en_US_news, boundary("word")))

  colnames(blog_word_count) <- c('blog_avg_word_count') #rename column
  colnames(twitter_word_count) <- c('twitter_avg_word_count') #rename column
  colnames(news_word_count) <- c('news_avg_word_count') #rename column

#Character Count
blog_character_count<-as.data.frame(nchar(en_US_blogs))
twitter_character_count<-as.data.frame(nchar(en_US_twitter))
news_character_count<-as.data.frame(nchar(en_US_news))

  colnames(blog_character_count) <- c('blog_avg_character_count') #rename column
  colnames(twitter_character_count) <- c('twitter_avg_character_count') #rename column
  colnames(news_character_count) <- c('news_avg_character_count') #rename column

#Create Summary Tables
blog_summary<-cbind(blog_character_count, blog_word_count)
twitter_summary<-cbind(twitter_character_count, twitter_word_count)
news_summary<-cbind(news_character_count, news_word_count)

blog_mean<-summarise_all(blog_summary, mean)
twitter_mean<-summarise_all(twitter_summary, mean)
news_mean<-summarise_all(news_summary, mean)

final_summary<-cbind(blog_mean, twitter_mean, news_mean)
final_summary

#Line count
blog_length<-length(en_US_blogs)
blog_twitter<-length(en_US_twitter)
blog_news<-length(en_US_news)

line_summary<-cbind(blog_length, blog_twitter, blog_news)
line_summary
```

# Exploratory Data Analysis 
A histogram for character count shows that blog and news are highly skewed, while twitter isn't as skewed, but does have an interesting shape that is non-normal. 
```{r}
p1<-ggplot(blog_summary, aes(x=blog_avg_character_count)) + 
  geom_histogram()+
  geom_histogram(binwidth=1)+
  ggtitle("twitter_character_count")
p2<-ggplot(twitter_summary, aes(x=twitter_avg_character_count)) + 
  geom_histogram(binwidth=1)+
  ggtitle("twitter_character_count")
p3<-ggplot(news_summary, aes(x=news_avg_character_count)) + 
  geom_histogram(binwidth=1)+
  ggtitle("twitter_character_count")
p1
p2
p3
```

